---
title: "CTC Enhanced Contribution Method"
output: html_notebook
---

# CTC Method

Exploration of estimating enhanced contribtution using data from the Chinook Technical Committee. Note these data are for Chinook only.
THIS ANALYSIS WAS NOT INCLUDED IN THE REPORT

## Data:

__Total annual catch:__
  *The Pacific Salmon Commission’s (PSC) Joint Chinook Technical Committee (CTC) Annual Report of Catch and Escapement contains tables of landed catch of Chinook salmon by region and gear type in Appendix A. The full dataset with all catch for all years was acquired through the CTC (downloaded by Andy from the CTC website)

__Total enhanced catch:__
  *Total annual returns of CWT Chinook were obtained from SEP’s EPAD (provided by Cheryl Lynch). Data were filtered to only include the stocks and stages used as CTC indicators to calculate an annual total indicator catch value and be able to match indicator catch to the total catch reported in the CTC reports.
  *The PSC’s CTC annual Exploitation Rate Analysis reports contain tables of the percent distribution of landed catch for exploitation rate indicator stocks by calendar year in Appendix C. The full dataset with mortality distributions for all years for indicator stocks in BC was acquired from the CTC website
  *Non-indicator catch: based off of hatchery release records from EPAD (provided by Joan Bateman), which were used to estimate the proportion of total hatchery releases that are CTC indicator releases
  
## Method: 
To determine enhanced contribution to total catch, I used a combination of CTC and EPAD data. Total catch by region/fishery was obtained from the CTC’s Annual Report of Catch and Escapement, Appendix A. In these reports, the fisheries are grouped into “Troll”, “Net”, and “Sport”, and have been separated into AABM and ISBM fisheries per region (AABM: SEAK, NBC, WCVI; ISBM: NBC & CBC, SBC, N Falcon, S Falcon, WAC, Puget Sound; Terminal: SEAK, Canada, SUS). Note that the American regions/fisheries were grouped as follows:
  
  *SEAK = SEAK AABM + SEAK Term
  *SUS = N Falcon ISBM + S Falcon ISBM + WAC ISBM + SUS Term

There is no stock information associated with the total catch data, but I needed to figure out what proportion of that total catch was made up of the CWT-based CTC indicator stocks. To do this, I filtered the EPAD CWT returns to only include CTC indicator stocks and extracted total annual returns (catch + escapement). To allocate each year’s return to the appropriate fishery or escapement, I multiplied the returns by the % distributions in the CTC’s mortality distribution tables (these tables show what proportion of the indicator stocks were captured in each fishery or made it to escapement each year). This gave me total indicator catch per region/fishery. It should be noted however that it is not entirely clear which fisheries go into the CTC total catch. I have made my best guess using their fishery key, however not all fisheries listed in the key were provided in the mortality distribution tables, so there may be some discrepancies if key fisheries are missing (this is being discussed with members of the CTC).
To account for hatchery catch of non-CTC indicators, I calculated the proportion of all hatchery releases that were indicator releases each year. I then plotted the figure and visually selected time periods where the proportion of releases that were indicators were similar. This resulted in the following proportions of indicators in releases:

1972-1977:	0.29
1978-1984:	0.87
1985-2003:	0.65
2004-2019:	0.76

I then used these proportions to expand the total indicator catch to the total enhanced catch by dividing the returns in each year by the associated proportion. This was then divided by total catch to get enhanced contribution to catch.

# CTC Code

```{r Import CTC Data, echo = FALSE}
# CTC CN catch
CTC_catch <- read_csv(here("raw", "CTC_totcatch.csv"))

# Mortality Distribution Tables from CN CTC
CTC_MDT <- read_csv(here("raw", "CTC_MDT.csv"))

```


```{r CTC Data Tidy}
# Reformat CTC catch data
CTC_dat <- CTC_catch %>%
  rename(year = Year, region = Fishery) %>%
  pivot_longer(cols = 3:8, names_to = "fishery", values_to = "overall_catch") %>%
  mutate(region = case_when(region == "NC BC ISBM" ~ "NCBC ISBM",
                            region == "PS -JDF" ~ "PS",
                           TRUE ~ region))

# Reformat mortality distribution table
CTC_MDT1 <- CTC_MDT %>%
  select(-c(2, 4:5, 34)) %>%
  rename(year = Catch.Year, stock = Stock, escapement = Escapement) %>%
  pivot_longer(cols = 3:30, names_to = "fishery", values_to = "catch") %>%
  select(1:2, 4:5, 3) %>%
  separate(fishery, c("type", "region", "fishery"), fill = "left") %>%
  mutate(stock = case_when(stock == "Lower Shuswap" ~ "Shuswap R Low",
                           stock == "Robertson" ~ "Robertson Cr",
                           stock == "Quinsam" ~ "Quinsam R",
                           stock == "Puntledge" ~ "Puntledge R",
                           stock == "Phillips" ~ "Phillips R",
                           stock == "Nicola" ~ "Nicola R", 
                           stock == "Nanaimo" ~ "Nanaimo R",
                           stock == "Middle Shuswap" ~ "Shuswap R Middle",
                           stock == "Kitsumkalum" ~ "Kitsumkalum R",
                           stock == "Harrison" ~ "Harrison R",
                           stock == "Dome" ~ "Dome Cr", 
                           stock == "Cowichan" ~ "Cowichan R",
                           stock == "Chilliwack" ~ "Chilliwack R",
                           stock == "Big Qualicum" ~ "Big Qualicum R",
                           stock == "Atnarko" ~ "Atnarko R",
                           TRUE ~ stock))

```

```{r Import EPAD Data, echo = FALSE}
# Expanded CWT catch data by fishery for CN from EPAD - all
CN_dat <- read_csv(here("raw", "CN_expanded_all.csv"))

# Expanded CWT catch data by fishery for CO from EPAD - all
CO_dat <- read_csv(here("raw", "CO_expanded_all.csv"))

# Bring in release data from EPAD
all_rel <- read_csv(here("raw", "All_SEP_releases.csv")) 
```



```{r EPAD Data Tidy}
# pull out total catch from EPAD
CN_EPAD <- CN_dat %>%
  select(project = PROJ_NAME, species = SPECIES_NAME, run = RUN_NAME, BY = BROOD_YEAR, stock = STOCK_NAME, CU = STOCK_CU_INDEX, facility = FACILITY_NAME, prod_area = PROD_AREA_CODE, stage = RELEASE_STAGE_NAME, tagcode = MRP_TAGCODE, OEY = RELEASE_YEAR, surv_code = SURVIVAL_CODE, expl_code = EXPLOIT_CODE, bio_code = BIOSTND_CODE, tottagged = TotTagged, totrel = TotRelease, age = Age, year = RecovYear, totcatch = TotCatch, escape = Escape, returns = `TotCatch+Esc`) %>%
  mutate(stock = case_when(stock %in% c("Atnarko R Low", "Atnarko R Up") ~ "Atnarko R", 
                           stock %in% c("Kitsumkalum R", "Kitsum Abv Canyon", "Kitsum Bel Canyon") ~ "Kitsumkalum R",
                           TRUE ~ stock)) %>%
  mutate(stock = case_when((stock == "Kitsumkalum R" & stage == "Smolt 1+") ~ "Kitsumkalum.Yearling",
                           (stock == "Atnarko R" & stage == "Smolt 1+") ~ "Atnarko.Yearling",
                           TRUE ~ stock)) %>%
  filter(!stage %in% c("Nat Sm 0+", "Seapen 0+", "Fed Fry", "Fed Fall", "Nat Fry", "Seapen 1+"), expl_code != "N")

# Pull out the relevant/indicator stocks by joining catch with MDT
CN_catch_dist <- left_join(CTC_MDT1, CN_EPAD[, c("stock", "stage", "year", "returns")], by = c("stock", "year")) %>%
  mutate(catch = catch/100, escapement = escapement/100)

# Isolate the stages that correspond with the indicators and then rejoin                           
CN_catch_dist_yearling <- CN_catch_dist %>%
  filter(stock %in% c("Kitsumkalum.Yearling", "Atnarko.Yearling", "Nicola R", "Dome Cr"))
CN_catch_dist_indicators <- CN_catch_dist %>%
  filter(stage != "Smolt 1+")
CN_catch_dist1 <- rbind(CN_catch_dist_yearling, CN_catch_dist_indicators) %>%
  mutate(type = replace_na(type, "AABM")) %>%
  unite(col = region, region, type, sep = " ", remove = T, na.rm = T)

# Ensure the EPAD catch and catch distribution have the same regions as the CTC catch data and then calculate tot catch and escapement using MDT values
CN_catch_dist <- CN_catch_dist1 %>%
  mutate(region = case_when(region %in% c("SEAK AABM", "SEAK Term") ~ "SEAK",
                           region %in% c("NF ISBM", "SF ISBM", "WAC ISBM", "SUS Term") ~ "SUS",
                           region == "PS ISBM" ~ "PS",
                           region == "CAN Term" ~ "CDN Term",
                           TRUE ~ region)) %>%
  group_by(stock, year, region, fishery) %>%
  mutate(totreturns = sum(returns), catch = sum(unique(catch))) %>%
  select(-returns) %>%
  distinct() %>%
  rowwise() %>%
  mutate(totcatch = catch*totreturns, totescape = escapement*totreturns) %>%
  group_by(year, region, fishery) %>%
  mutate(comb_ind_catch = sum(totcatch, na.rm = T))

CN_ind_catch <- CN_catch_dist %>%
  select(year, region, fishery, comb_ind_catch) %>%
  distinct()

# Estimate enhanced contribution of indicators to total catch
CN_catch_indcontr <- left_join(CTC_dat, CN_ind_catch) %>%
  mutate(ind_contr = comb_ind_catch/overall_catch) %>%
  filter(ind_contr < Inf)

ggplot(CN_catch_indcontr, aes(x = year, y = ind_contr, fill = fishery)) +
  geom_bar(position = "dodge", stat = "identity") +
  facet_wrap(~region, scales = "free_y")

```


```{r CTC Enh Contr}
rel <- all_rel %>%
  select(species = SPECIES_NAME, stock = STOCK_NAME, stage = RELEASE_STAGE_NAME, region = STOCK_PROD_AREA_CODE, relY = RELEASE_YEAR, tagcode = MRP_TAGCODE, tagged = TaggedNum, nonCWT_mark = NoTagNum, unmrk = UnmarkedNum, totrel = TotalRelease, exp_code = EXPLOIT_CODE) %>%
  mutate(stock = case_when(stock %in% c("Atnarko R Low", "Atnarko R Up") ~ "Atnarko R", 
                           stock %in% c("Kitsumkalum R", "Kitsum Abv Canyon", "Kitsum Bel Canyon") ~ "Kitsumkalum R",
                           TRUE ~ stock)) %>%
  mutate(stock = case_when((stock == "Kitsumkalum R" & stage == "Smolt 1+") ~ "Kitsumkalum.Yearling",
                           (stock == "Atnarko R" & stage == "Smolt 1+") ~ "Atnarko.Yearling",
                           TRUE ~ stock)) %>%
  filter(species == "Chinook", exp_code != "N")

# Isolate the stages that correspond to the indicators and then rejoin
yearling_rel <- rel %>%
  filter(stock %in% c("Kitsumkalum.Yearling", "Atnarko.Yearling", "Nicola R", "Dome Cr"), stage == "Smolt 1+")
smolt_rel <- rel %>%
  filter(stage == "Smolt 0+")
rel2 <- rbind(yearling_rel, smolt_rel)

# pull out indicator stocks and only look at those that were CWT'd
ind_rel <- left_join(CTC_MDT1[, c("stock")], rel2, by = "stock") %>%
  distinct() %>%
  mutate(nonCWT_mark = as.numeric(nonCWT_mark), tagged = as.numeric(tagged)) %>%
  replace_na(list(tagged = 0, nonCWT_mark = 0, unmrk = 0)) %>%
  mutate(unmrk = nonCWT_mark + unmrk) %>%
  mutate(mrk = totrel-unmrk) %>%
  mutate(mark_type = case_when(startsWith(tagcode, "R") ~ "non-CWT",
                               startsWith(tagcode, "NO") ~ "non-CWT",
                               startsWith(tagcode, "L") ~ "non-CWT",
                               startsWith(tagcode, "H") ~ "non-CWT",
                               startsWith(tagcode, "D") ~ "non-CWT",
                               startsWith(tagcode, "AD") ~ "non-CWT",
                               startsWith(tagcode, "B") ~ "non-CWT",
                               TRUE ~ "CWT")) %>%
  filter(mark_type != "non-CWT") %>%
  select(relY, totrel) %>%
  group_by(relY) %>%
  summarise(indrel = sum(totrel, na.rm = T)) %>%
  filter(relY != 'NA')

# annual releases overall
all_rel <- rel %>%
  select(relY, totrel) %>%
  distinct() %>%
  group_by(relY) %>%
  summarise(totrel = sum(totrel, na.rm = T))

# proportion of overall releases that were indicators, then look at how proportion changes over time and calculate median for various time periods
ind_prop_releases <- full_join(ind_rel, all_rel) %>%
  mutate(ind_prop = indrel/totrel) %>%
  mutate(mean_prop = case_when(relY %in% c(1972:1977) ~ 0.29,
                              relY %in% c(1978:1984) ~ 0.87,
                              relY %in% c(1985:2003) ~ 0.65,
                              relY %in% c(2004:2019) ~ 0.76)) %>%
  #let's assume they mostly come back as 3 year olds to help line up the rel years and recovery years
  mutate(year = relY + 3)

# Plot proportion of releases that were indicators
ggplot(ind_prop_releases, aes(x = relY, y = ind_prop)) +
  geom_col()
  
# Now use the above proportion to estimate total enhanced contribution by region
CN_catch_contr_region <- left_join(CN_catch_indcontr, ind_prop_releases[,c("year", "mean_prop")], by = "year") %>%
  mutate(enhanced_catch = comb_ind_catch/mean_prop) %>%
  group_by(year, region) %>%
  mutate(tot_catch = sum(overall_catch), tot_hatch = sum(enhanced_catch)) %>%
  select(year, region, tot_catch, tot_hatch) %>%
  distinct() %>%
  mutate(enhctr = tot_hatch/tot_catch) %>%
  mutate(region = factor(region, levels = c("SEAK", "NBC AABM", "NCBC ISBM", "SBC ISBM", "WCVI AABM", "CDN Term", "PS", "SUS"))) %>%
  filter(enhctr < 1)

mean_enhctr_region_CTC <- CN_catch_contr_region %>%
  group_by(region) %>%
  summarise(mean_enhctr = mean(enhctr), sd = sd(enhctr))

# Plot total enhanced contribution by region/fishery
ggplot(CN_catch_contr_region, aes(x = year, y = enhctr)) +
  geom_col() +
  facet_wrap(~region, scales = "free_y") +
  theme_bw() +
  labs(y = "Enhanced Contribution")
#ggsave("../figs/harvest/totcatch/CTC_enhctr_regional.png", width = 18, height = 14, units = "cm")



# Now use the above proportion to estimate total enhanced catch of Chinook and calculate enhanced contribution to total catch by fishery (i.e. Net, Troll, Sport) by region
CN_catch_contr <- left_join(CN_catch_indcontr, ind_prop_releases[,c("year", "mean_prop")], by = "year") %>%
  mutate(enhanced_catch = comb_ind_catch/mean_prop) %>%
  mutate(enhanced_contr = enhanced_catch/overall_catch) %>%
  filter(enhanced_contr < 10)

mean_enhctr_CTC <- CN_catch_contr %>%
  #filter(enhanced_contr < 1) %>%
  group_by(region, fishery) %>%
  summarise(mean_enhctr = mean(enhanced_contr), sd = sd(enhanced_contr))
  
ggplot(CN_catch_contr, aes(x = year, y = enhanced_contr, fill = fishery)) +
  geom_bar(position = "dodge", stat = "identity") +
  facet_wrap(~region, scales = "free_y") +
  theme_bw()

```